Different end times in survival data

### 2024-07-19 text/24/different-end-times.Rmd
Added missing-semicolon

```{r different-end-times-02}
sim %>%
  group_by(g) %>%
  summarize(
    n_0_to_190=sum(raw_time <= 190),
    n_191_to_225=sum(raw_time > 190&raw_time<=225),
    n_above_225=sum(raw_time > 225)) -> sim_counts
sim_counts
```

There are indeed more events at a threshold of 190 or below in group B (`r sim_counts$n_0_to_190[2]`) than there are in group A (`r sim_counts$n_0_to_190[1]`). There are, as well, more events at a threshold of 225 and below in group B (`r 100-sim_counts$n_above_225[2]`) than there are in group A  (`r 100-sim_counts$n_above_225[1]`).

There are `r sim_counts$n_191_to_225[1]+sim_counts$n_191_to_225[1]` events that are in the "Twilight Zone". This means that `r sim_counts$n_191_to_225[1]` of the Twilight Zone events in group A are censored, while `r sim_counts$n_191_to_225[2]` of the Twilight Zone events in group B are still counted as events.

@@

What if you set the censoring times to 190 days for both groups? That effectively converts `r sim_counts$n_191_to_225[2]` patients in the second group from events to observations censored at 190 days.

>>>>

```{r different-end-times-02}
sim %>%
  mutate(
    n_0_to_190 =
      as.numeric(raw_time <= 190)) %>%
  mutate(
    n_191_to_225 =
      as.numeric((raw_time > 190) & (raw_time<=225))) %>%
  mutate(
    n_above_225 =
      as.numeric(raw_time > 225)) %>%
  group_by(g) %>%
  summarize(
    n_0_to_190=sum(n_0_to_190),
    n_191_to_225=sum(n_191_to_225),
    n_above_225=sum(n_above_225)) %>%
  data.frame -> sim_counts
sim_counts

```

There are several events that are in the "Twilight Zone". The Twilight Zone events in group A are censored, while the Twilight Zone events in group B are still counted as events.

@@

What if you set the censoring times to 190 days for both groups? That effectively converts patients in the Twilight Zone in the second group from events to observations censored at 190 days.
